On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 bqp.tex
Break nested lemma/proof

\begin{thm}
	\Ethan{Main theorem of the section}
	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
\end{thm}

We'll construct this protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.

@@

\begin{rmk}
	The same construction works for $\FBQP$ too. \Ethan{maybe say more?}
\end{rmk}

>>>>

\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
\end{thm}

We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.

@@

\begin{rmk}
	The same construction works for $\FBQP$ too.
	\Ethan{Maybe say more? Where should I define $\FBQP$?}
\end{rmk}

### 2020-02-05 hamiltonian.tex
Break nested lemma/proof

\subsection{Reducing quantum circuit to  local Hamiltonian }

@@

	To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
	$$K_{clock}=\ker H_{clock}$$
	$$K_{in}=\ker H_{in}$$
	$$K_{prop}=\ker H_{prop}$$
	It is clear that $K_{clock}$ consists of the states with time registers of the form $\ket{\hat{t}}$.

	\begin{lemma} \hannote{throw outside? or just merge}
		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
	\end{lemma}

	\begin{proof}
		Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$. So we can obtain the required statement by induction.
	\end{proof}

	\begin{corollary}
		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$
	\end{corollary}

>>>>

\subsection{Reducing quantum circuit to local Hamiltonian}

@@

	To properly combine the three Hamiltonians defined and analyze it using the projection lemma (\cref{thm:projection}), we consider the kernels of the Hamiltonians we defined.
	$$K_{clock}=\ker H_{clock}$$
	$$K_{in}=\ker H_{in}$$
	$$K_{prop}=\ker H_{prop}$$

	Clearly,
	$$K_{clock}=\set{\sum_{t=1}^T \ket{\phi_t}\otimes\ket{\hat{t}}:\ket{\phi_t}\in\cB^{\otimes n}}$$
	Let $\ket\phi\in K_{clock}\cap K_{prop}$.
	Consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$.
	As $\ket\phi\in K_{prop}$, we can then do induction using $\widetilde{t}$ as base case to get the relations between the $\ket{\phi_t}$s and conclude that $\ket\phi$ must have the form:
	$$\ket\phi=\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}$$
	$$\Rightarrow K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$

	As a direct result, we get
	$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$$
